
## Updated Simulation ##


```{r}
library(rstan)
library(updog)
```

```{r}
vbmodel <- rstan::stan_model(file = "./vargeno.stan", )
```

```{r}
get_maxgeno <- function(postprobmat) {
  apply(postprobmat, 1, which.max) - 1
}
```

```{r}
lgeno <- function(x) {
  postprobmat <- matrix(summary(x, pars = "logpostprobmat")$summary[, "mean"], ncol = ploidy + 1, byrow = TRUE)
  rowmax <- apply(postprobmat, 1, max)
  postprobmat <- postprobmat - rowmax
  postprobmat <- exp(postprobmat - log(rowSums(exp(postprobmat))))
  return(postprobmat)
}
```


**Simulate the dataframe**
```{r}
itermax <- 100
bias_vec <- c(1)
seq_vec  <- 0.01
od_vec   <- c(0)
itervec  <- seq_len(itermax)
ploidy_vec <- 6
allele_vec <- c(0.5, 0.9)
nsamp_vec <- c(30)
recount_vec <- c(100)
paramdf <- expand.grid(bias = bias_vec,
                       seq = seq_vec, 
                       od = od_vec, 
                       iter = itervec, 
                       allele = allele_vec, 
                       nsamp = nsamp_vec, 
                       recount = recount_vec, 
                       ploidy = ploidy_vec)
```

```{r}
paramdf
```

**Simulate data from extracting the index from the dataframe**
```{r}
simulate = function(item) {
  
    current_bias = paramdf[item, "bias"]
    current_seq = paramdf[item, "seq"]
    current_od = paramdf[item, "od"]
    current_allele = paramdf[item, "allele"]
    nsamp = paramdf[item, "nsamp"]
    recount = paramdf[item, "recount"]
    ploidy = paramdf[item, "ploidy"]
  
    
    return(list(current_bias = current_bias, 
                current_seq = current_seq, 
                current_od = current_od, 
                current_allele = current_allele, 
                nsamp = nsamp, 
                recount = recount, 
                ploidy = ploidy))
  
}

```

**Simulate the item value**
```{r}
item = sample(1:nrow(paramdf), 1)

item
```

**Create a list based on the simulation**
```{r}
sim_list = simulate(item)

sim_list
```

**Use the values from the simulations**
```{r}
seq = sim_list$current_seq
bias = sim_list$current_bias
od = sim_list$current_od
ploidy = sim_list$ploidy
recount = sim_list$recount
nsamp = sim_list$nsamp
allele_freq = sim_list$current_allele
```

**Simulate genovec using rgeno**
```{r}
genovec <- rgeno(n           = nsamp,
                 ploidy      = ploidy,
                 model       = "hw",
                 allele_freq = allele_freq)

genovec
```

**Simulate sizevec using recount**
```{r}
sizevec = rep(sim_list$recount, sim_list$nsamp)

sizevec
```

**Simulate refvec**
```{r}
refvec <- rflexdog(sizevec = sizevec,
                   geno    = genovec,
                   ploidy  = ploidy,
                   seq     = seq,
                   bias    = bias,
                   od      = od)

refvec
```

**Write the standog function**
```{r}
standog = function(refvec, sizevec, ploidy) {
  vbout <- rstan::vb(object = vbmodel, data = list(K = ploidy, N = nsamp, x = refvec, n = sizevec))
  
  postprobmat <- lgeno(vbout)

  stan_geno <- get_maxgeno(postprobmat)
  
  return(list(postprobmat = postprobmat, geno = stan_geno))
  
}
```

**Simulate results from standog**
```{r}
sout = standog(refvec = refvec, sizevec = sizevec, ploidy = ploidy)
```

**Simulate results from updog**
```{r}
uout <- flexdog(refvec = refvec, sizevec = sizevec, ploidy = ploidy, model = "hw")
```

**Extract simulated genotypes from updog and standog**
```{r}
updog_geno = uout$geno
standog_geno = sout$geno
```

**Calculate the misclassification error for stan**
```{r}
stan_classification_error = mean(genovec != standog_geno)

stan_classification_error
```

**Calculate the misclassification error for updog**
```{r}
updog_classification_error = mean(genovec != updog_geno)

updog_classification_error
```

**Difference between updog and standog**
```{r}
mean(standog_geno != updog_geno)
```






























